\clearpage
\section*{ABSTRACT}
\label{ozeten}

Today, REST API structures are widely used in web applications, mobile systems, microservice architectures, and cloud-based platforms. As API usage increases, security vulnerabilities have become a significant threat to modern software systems. In particular, broken authentication, authorization flaws, IDOR/BOLA vulnerabilities, mass assignment issues, and insufficient security controls may allow attackers to escalate privileges, access sensitive data, and perform critical operations. In this project, the ``API Fortress'' system was designed as an educational attack and defense simulation laboratory for learning REST API security vulnerabilities in a practical way. The system consists of two main environments: an insecure API environment and a secure API environment. In the insecure environment, intentionally implemented vulnerabilities allow students to reach CTF-like objectives, while the secure environment demonstrates how the same vulnerabilities are mitigated through proper defense mechanisms. Within the scope of the project, several vulnerability scenarios were implemented, including privilege escalation through Mass Assignment, authentication bypass using a hidden header, Broken Authentication caused by missing password validation, IDOR/BOLA for accessing other users' data, and Broken Function Level Authorization for unauthorized user deletion. In the secure version, JWT-based authentication, role-based authorization, rate limiting, a regex-based Web Application Firewall (WAF), secure password hashing, and input validation mechanisms were developed. Python, the Flask framework, SQLAlchemy ORM, and a Docker-based development environment were used during the implementation process. The tests showed that API Fortress provides a functional laboratory environment for practical REST API security education. This study aims to improve secure software development awareness and make the relationship between attack and defense mechanisms in API security more understandable.

\vspace{3mm}

\noindent \textbf{Keywords:} REST API, API Security, OWASP API Security, CTF, Flask, JWT, WAF, IDOR, Mass Assignment, Docker, SQLAlchemy

\clearpage