\renewcommand\bibsection{\centering\section*{\large KAYNAKLAR}}
\begin{thebibliography}{99}
\makeatletter
\renewcommand*{\@biblabel}[1]{[#1]\hspace{1cm}}
\makeatother

\bibitem{owasp2023}
OWASP Foundation. (2023). OWASP API Security Top 10 2023. OWASP API Security Project.

\bibitem{fielding2000}
Roy Thomas Fielding (2000). Architectural Styles and the Design of Network-based Software Architectures (Doctoral dissertation). University of California, Irvine.

\bibitem{rfc7519}
Michael Jones, John Bradley, \& Nat Sakimura (2015). RFC 7519: JSON Web Token (JWT). Internet Engineering Task Force (IETF).

\bibitem{flask2024}
Flask Documentation. (2024). Flask Web Framework.

\bibitem{sqlalchemy2024}
SQLAlchemy Documentation. (2024). SQLAlchemy ORM and Database Toolkit.

\bibitem{docker2024}
Docker. (2024). Docker Documentation.

\bibitem{jensen2019}
M. Jensen, Nils Gruschka, \& Ralf Herkenhöner (2019). A Survey of Attacks on Web Services and Countermeasures. International Journal of Web Information Systems, 15(3), 224--246.

\bibitem{portswigger2024}
PortSwigger. (2024). Web Security Academy.

\bibitem{juiceshop2023}
OWASP Foundation. (2023). OWASP Juice Shop Project.

\bibitem{vargas2020}
Carlos Vargas, Mohamed Emam, \& Nils Ruehlen (2020). REST API Security Vulnerabilities in Practice: An Empirical Study. In Proceedings of the IEEE International Conference on Software Quality, Reliability and Security, 87--97.

\bibitem{owaspdoc2024}
OWASP Foundation. (2024). OWASP API Security Project Documentation.

\bibitem{jwtio2024}
JSON Web Token Introduction. (2024). JWT.io Documentation.

\bibitem{auth0jwt2024}
Auth0. (2024). JSON Web Tokens Documentation.

\bibitem{portswiggerapi2024}
PortSwigger. (2024). API Testing and OWASP Top 10 Vulnerabilities.

\bibitem{owasp2023ed}
OWASP Foundation. (2023). OWASP API Security Top 10 -- 2023 Edition.

\end{thebibliography}
\clearpage
